### 2011-09-25 doc/theses/vitasek/chapter-1-definitions.tex
Thesis: in progress.

Furthermore, we denote $I$ % TODO fix the capital I
the set of all ids and $V$ % TODO fix the capital V
the set of all values in the document. We will need two more definitions from the article.

@@

\section{XML Keys}

TODO

\subsection{According to Specification}

TODO compare them to ID attributes

\subsection{According to \cite{keX}}

TODO show how a XML key is defined using the keX notation % this is a terrible sentence

@@

\begin{define}[Attribute mapping]
	For $x \in \Sigma^E$ and $y \in \Sigma^A$ we define the \textit{attribute mapping} of y over x, denoted $M_{x}^{y}$, the $I \times I$ % TODO fix the capital I
	relation defined by
	\[M_{x}^{y} = \{ (z,w): label(z) = x, label(w) = y, parent(w) = z \}\]
\end{define}

@@

\subsection{Attribute Mapping Model}

TODO

\section{ID Set}

@@

\begin{define}[ID set]
A set of candidate attribute mappings $I = \{m_1, \ldots m_n\}$ is an ID set iff
\[\bigcap_{m_i \in I} \tau(m_i) = \emptyset \wedge \bigcap_{m_i \in I} \iota(m_i) = \emptyset\]
\end{define}

@@

\subsection{IDREF and IDREFS Attributes}

TODO

\section{Attribute Mapping Weight}

TODO this is from FIDAX again

$M = \{m_1, \dots m_i\}$ is the set of all non-empty AMs in the document.

@@

TODO example

@@

TODO example

>>>>

Furthermore, we denote $\mathcal{I}$ the set of all ids and $\mathcal{V}$ the set of all values in the document. We will need two more definitions from the article.

@@

%\section{XML Keys} - is this necessary at all?

%TODO

%\subsection{According to Specification}

%TODO compare them to ID attributes

%\subsection{According to \cite{keX}}

%TODO show how a XML key is defined using the keX notation % this is a terrible sentence

@@

\begin{define}[Attribute mapping]
	For $x \in \Sigma^E$ and $y \in \Sigma^A$ we define the \textit{attribute mapping} of y over x, denoted $M_{x}^{y}$, the $\mathcal{I} \times \mathcal{I}$ relation defined by
	\[M_{x}^{y} = \{ (z,w): label(z) = x, label(w) = y, parent(w) = z \}\]
\end{define}

@@

\paragraph{Attribute Mapping Model}
An attribute mapping model is a data structure containing the information about all the AMs in a document, together with their images. We shall use this notion later in experimental part of this work.

\section{ID Set}
\label{section-definitions-id-set}

@@

\begin{define}[ID set]
A set of candidate attribute mappings $I = \{m_1, \ldots m_n\}$ is an \textit{ID set} iff
\[\bigcap_{m_i \in I} \tau(m_i) = \emptyset \wedge \bigcap_{m_i \in I} \iota(m_i) = \emptyset\]
\end{define}

@@

\subsection{IDREF and IDREFS Condition}

Given an ID set $I$, the requirements from Section \ref{section-definitions-id-attributes} give us the following condition for an attribute mapping $m$ to be marked IDREF.
\[\iota(m) \subseteq \bigcup_{m_i \in I} \iota(m_i)\]
Furthermore if $m$ contains multivalued attributes, it is to be marked IDREFS.

\section{Attribute Mapping Weight}
\label{section-definitions-weight}

This definition of weight for AMs or AM sets comes from \cite{fidax} again.

Let $M = \{m_1, \dots m_i\}$ be the set of all non-empty AMs in the document.

@@

From the cited article:
\begin{quote}
The support of attribute mapping $M_x^y$ is the fraction of edges in the XML tree that connect $x$ elements to $y$ attributes.
\end{quote}

\paragraph{Example}
Support of $M_{y}^{a}$ in our example is $2 / (2+1+1+1) = 0.4$. Support of every other mapping is $1 / (2+1+1+1) = 0.2$.

@@

Again from the article:
\begin{quote}
The coverage of an attribute mapping measures how much of the image of that mapping occurs elsewhere, as a fraction of all mappings images in the document.
\end{quote}

\paragraph{Example}
Coverage of $M_{y}^{a}$ in our example is $(0+0+1) / (2+1+1+1) = 0.2$. Coverage of $M_{z}^{a}$ is $0.2$ as well, all the other mappings have coverage $0$.
\\

\textit{Weight} of an attribute mapping is then defined as a linear combination of its support and coverage.

\begin{define}[Weight]
For $\alpha, \beta \geq 0$ as relative priorities of support and coverage we define the AM \textit{weight} as follows.
\[weight(m) = \alpha . \phi(m) + \beta . \chi(m)\]
For a set of AMs (which may or may not be an ID set) $S = \{m_1, \ldots m_i\}$ we define the weight of this set as the sum of the weights of its AMs.
\[weight(S) = \sum_{m \in S} weight(m)\]
\end{define}

\section{Independent Set}

We shall need the notion of an indepentent set of vertices in a graph and its weighted variant.

\begin{define}[Independent set]
Given an undirected graph $G = (V, E)$, a set of vertices $I \subseteq V$ is an \textit{independent set}, iff the following holds.
\[\forall v_1, v_2 \in I, v_1 \neq v_2: (v_1, v_2) \notin E \]
\end{define}

\begin{define}[Maximum weighted independent set]
Given an undirected graph $G = (V, E)$ and a weight function $w: V \rightarrow \mathbb{R}$, an independent set $I_{max}$ is the \textit{maximum weighted independent set}, iff the following is satisfied.
\[\forall I' \subseteq V, I' \text{is an independent set}: \sum_{v \in I'} w(v) \leqslant \sum_{v in I_{max}} w(v)\]
\end{define}

TODO finding this is NP-hard - cite

\section{Linear Programming}

TODO define LP rigorously

\begin{eqnarray*}
\max_{x} z & = & \mathbf{c}^{\mathrm{T}}\mathbf{x} \\
s.t.\, A\mathbf{x} & \leqslant & \mathbf{b} \\
\mathbf{x} & \geqslant & 0 \\
\end{eqnarray*}
\[
\mathbf{x} =
\begin{bmatrix}
x_1 \\
x_2 \\
\ldots \\
x_n \\
\end{bmatrix},
\mathbf{c} = 
\begin{bmatrix}
c_1 \\
c_2 \\
\ldots \\
c_n \\
\end{bmatrix},
\mathbf{b} =
\begin{bmatrix}
b_1 \\
b_2 \\
\ldots \\
b_m \\
\end{bmatrix}
\]

Where $\mathbf{x}$ is the vector of variables (to be found by the optimization), $\mathbf{b}$ is the vector and $A$ is the accompanying matrix of constraints and $\mathbf{c}$ is the vector of coefficients for the objective function. $\mathbf{x}$ and $\mathbf{c}$ have length $n$, $\mathbf{b}$ has length $m$ and $A$ has dimensions $m \times n$.

Another way to write this formulation is in the following.

\begin{eqnarray*}
\max_{x} z = \sum_{i=1}^{n} c_i x_i \\
s.t.\, a_{11}x_{1} + a_{12}x_{2} + \ldots + a_{1n}x_{n} & \leqslant & b_{1} \\
	   a_{21}x_{1} + a_{22}x_{2} + \ldots + a_{2n}x_{n} & \leqslant & b_{2} \\
	   \ldots \\
	   a_{m1}x_{1} + a_{m2}x_{2} + \ldots + a_{mn}x_{n} & \leqslant & b_{m} \\
	   x_i \geqslant 0, i = 1, \ldots n \\
\end{eqnarray*}

TODO it is possible to formulate minimization function

### 2011-09-25 doc/theses/vitasek/chapter-2-research.tex
Thesis: in progress.

According to the article \cite{fidax}, ...

TODO talk about FIDAX
To the best of our knowledge, there are no other articles dealing with this problem.

TODO talk about Fajt - but that's different, that's keys
TODO add citation for Fajt

\section{Independent Set}

TODO define IS + MIS rigorously

@@

>>>>

According to the article \cite[Chapter~4]{fidax}, the problem of finding an ID set (Section \ref{section-definitions-id-set}) with the maximal weight (Section \ref{section-definitions-weight}) is NP-hard. The article suggests a heuristic approach described in Section \ref{section-mip-fidax}, which was incorporated into the framework proposed by this work.

To the best of our knowledge, there are no other articles dealing with this problem.

TODO talk about Fajt \cite{fajt} - but that's different, that's keys. Sometimes, it is translatable, but not always.

@@

TODO LP is simple using Simplex method, however gets hard as soon as we require some of the variables to be integral or boolean.
